AFQ-Insight

### 2019-12-01 reports/manuscript/sections/conclusion.tex
Starting to work on figure captions.

We present here a novel method for analysis of dMRI tractometry data. This
method relies on the Sparse Group Lasso \cite{simon2013sparse} to provide both
acurate prediction of the phenotypic properties of individual subjects based on
their dMRI data, but also provides interpretable results by identifying the
features that are important across subjects to make these predictions. The
method is broadly applicable: it performs well in predicting both continuous
variables, such as biological age, as well as discrete variable, such as whether
a person is a patient or a healthy control. In both of these cases, SGL
out-performs previous algorithms that have been developed for these tasks. In
addition, the nested cross-validation approach that we have developed tunes the
degree of sparseness required by the algorithm, such that both very local
phenomena, as well as widely distributed phenomena are accurately captured.

>>>>

We present here a novel method for analysis of dMRI tractometry data. This
method relies on the Sparse Group Lasso \cite{simon2013sparse} to provide both
accurate prediction of the phenotypic properties of individual subjects based on
their dMRI data, but also provides interpretable results by identifying the
features that are important across subjects to make these predictions. The
method is broadly applicable: it performs well in predicting both continuous
variables, such as biological age, as well as discrete variable, such as whether
a person is a patient or a healthy control. In both of these cases, SGL
out-performs previous algorithms that have been developed for these tasks. In
addition, the nested cross-validation approach that we have developed tunes the
degree of sparseness required by the algorithm, such that both very local
phenomena, as well as widely distributed phenomena are accurately captured.

### 2019-12-01 reports/manuscript/sections/results.tex
Starting to work on figure captions.

\subsection*{Regression for age prediction}

The WH dataset used for continuous regression contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. SGL was fit to tractometry-extracted features: FA
and MD in 20 major brain tracts, with each tract divided into 100 nodes. To
evaluate the fit of the model, we used a nested cross-validation procedure. In
this procedure, batches of subjects are held out. For each batch (or fold), the
model is fully fit without this data. Then, once the parameters are fixed, the
model is inverted to predict the ages of held out subjects based on the linear
coeffiecients and the static non-linearity. data is held out, and a model age
was predicted using a model that was fit without that subject. This scheme
automatically finds the right level of regularization and fits the coefficients
to the ill-posed linear model, while guarding against overfitting. SGL
accurately predicts the age of the subjects in this procedure, with procedure,
with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}),
which is lower than the results of a recent study that predicted age in a large
sample, based on TBSS-extracted diffusion features \cite{Richard2018-ux}. The
model weights in this case are distributed over many different tracts and dMRI
tissue properties (Figure \ref{fig:regress-beta}) This demonstrates that SGL is
not coerced to produce overly sparse results when a more accurate model requires
a dense selection of features.

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\textwidth]{regression_residuals.png}
    \caption{{\bf Prediction of brain age.}
    }
    \label{fig:regress-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.5\textwidth]{regression_beta_annotated.pdf}
    \caption{{\bf Feature importance for brain age.}
    }
    \label{fig:regress-beta}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\textwidth]{regression_tract_profiles.pdf}
    \caption{{\bf Coefficients in context}
    It makes sense
    }
    \label{fig:regress-profiles}
\end{figure}

>>>>

\subsection*{SGL of tractometry data in a regression setting}

The WH dataset used for continuous regression contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. In this case, biological age was used as the
predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
tractometry-extracted features: FA and MD in 20 major brain tracts, with each
tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
cross-validation procedure. In this procedure, batches of subjects are held out.
For each batch (or fold), the model is fully fit without this data. Then, once
the parameters are fixed, the model is inverted to predict the ages of held out
subjects based on the linear coeffiecients and the static non-linearity. data is
held out, and a model age was predicted using a model that was fit without that
subject. This scheme automatically finds the right level of regularization and
fits the coefficients to the ill-posed linear model, while guarding against
overfitting. SGL accurately predicts the age of the subjects in this procedure,
with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}). This
is lower than the results of a recent study that predicted age in a large
sample, based on diffusion MRI features \cite{Richard2018-ux}. The model weights
in this case are distributed over many different tracts and dMRI tissue
properties (Figure \ref{fig:regress-beta}). This demonstrates that SGL is not
coerced to produce overly sparse results when a more accurate model requires a
dense selection of features.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{regression_residuals.png}
    \caption{{\bf Predicting age with tractometry and SGL.} Left: The predicted age of each individual (on the abscissa) and true age (on the ordinate), an accurate prediction falls close to the $y=x$ line (dashed). The mean absolute error in this case  is 3.6 years and, the coefficient of determination $R^2=0.3$. Right: Standardized residuals (on the abscissa) as a function of the true age (on the ordinate). Predictions are generally more accurate for younger individuals.
    }
    \label{fig:regress-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with the anterior up. The left cingulum cingulate (A) and forceps minor (B) are highlighted. Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
    }
    \label{fig:regress-beta}
\end{figure}
